Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages

### 2021-06-09 paper/manuscript.Rmd
New analysis with different subdataset

---
title: "Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages"
author: "Alain Danet, Maud Mouchet, Loubna El Madouri, Colin Fontaine (ordre non fixé)"
self_contained: yes
date: "`r Sys.Date()`"
tables: yes
bibliography: references.bib 
fontsize: 12pt
output:
  bookdown::html_document2:
    fig_caption: true
    theme: "journal"
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE 
)
```

@@

theme_set(mytheme)
```
```{r}
net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
```

@@

Biodiversity to affect ecosystem properties such as total biomass, productivity
and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. Numerous
studies have shown the decline of population and community biomass
[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
as ongoing extinction [@barnosky_]. Consequences of such trends on various
aspects of community structure are not well known whereas numerous ecological studies
have shown that the different aspects of community structure are tightly linked [REF].

The link between Biodiversity and ecosystem functioning is one of the most
famous example, experimental studies are in accordance to show a positive
relationship between species richness and community biomass
[@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But this relation is
not always found in natural settings [@grace_integrative_2016;
@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Also, numerous
studies have found relation between species richness and evenness, showing that
communities become more or less even as species richness increase
[@soininen_relationship_2012; @ma_species_2005;
@maureaud_biodiversityecosystem_2019], highlighting the diversity of
assembly processes in ecological communities.

The distribution and the number of ecological interactions, i.e. the structure
of ecological networks, also covary. In food-web, connectance, which measures the
degree of generalism in a network, has been theoretically shown to theoretically
positively scale with community biomass [@thebaut_food-web_2003]. Connectance
has been also shown to be negatively related to species richness in empirical
food-webs [@dunne_network_2006]. Trophic level has also been shown to be
positively linked to total biomass in theoretical models
[@wang_biodiversity_2018]. All together, these studies show that the
different dimensions of network structure are closely linked.

The space for time substitution allows to use the studies mentioned above to
predict how changes in species richness or community biomass will in turn affect
community and network structure. The hypothesis that space can be use to
surrogate space is often implicitly made in ecological studies. This method
began to be widely used in the early 20th century to infer the temporal
succession of vegetation from space variations [@pickett_space-time_1989].  It
supposes a homology between variations in space and in time i.e. that spatial
sequence corresponds to temporal sequences. This methods have raised criticisms
[@damgaard_critique_2019], with studies showing the coherent in space and time
[@blois_space_2013] or not [@johnson_testing_2008; @adler_contrasting_2007].
Spatial turnover of species composition, dispersal limitation, disturbance and
stochastic processes  has been hypothesised to be responsible for the failure of
space for time substitution [@adler_contrasting_2007; @blois_space_2013].

In this line, how biomass and species richness temporal trends are linked to
change in food-web structure is still an open question, as well as if space for
time substitution works in food-web assembly. The increasing availability of
ecological temporal series makes possible to assess those questions.

Using a standardized monitoring of fish freshwater communities on the period
1995-2018, we assessed the relationships among temporal trends of food-web
structure, trends of community biomass and trends in species richness.  
Moreover, we tested if the those relationships differs between communities that
lossed or gained biomass/species richness across time, reflecting potential
difference between disassembly and assembly processes. We finally assessed if
spatial relationships display the same patterns than temporal ones, to assess
the validity of space for time substitution.

@@

We characterized food-webs by its connectance, describing the degree of
generalism in a network [@dunne_network_2006, @delmas_analysing_2019]. It is
computed as the ratio between the actual number of links and the number of
potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
$S$ the number of trophic species). We also computed the average trophic level,
weighted by the biomass of the trophic species. The trophic level of a trophic
species is computed recursively as 1 added to the mean trophic level of the
preys that it consumes.

@@

```{r}
loadd(com_analysis_data, full_data2, st_mono_trends_combined_list)
```
```{r}
nb_st <- unique(full_data2$station) %>% length
nb_st_var <- map_dbl(st_mono_trends_combined_list$station, length) 
names(nb_st_var) <- st_mono_trends_combined_list$variable
```

@@

With the goal to characterize the links among the temporal variations of network
and community structure and the temporal variations of community biomass and
species richness, we characterized the temporal trajectories of network and
community structure at each site. We used a method based on second order
polynomial which allows to assess both the direction and the monotony of
temporal trends [@rigal_method_2020]. To avoid complex variations of biomass and
species richness, we selected the stations that displayed monotonic trends for
theses variable. Over the `r nb_st` stations, the selection procedure resulted
in respectively `r nb_st_var["log_bm_std"]` stations  and `r nb_st_var["log_rich_std"]`
for community biomass and species richness analysis.

@@

With the aim to test (1) the relationship among the temporal dynamics of network
structure from one side and species richness and community biomass from another
side, (2) if those relationships were different if the communities were
assembling or disassembling, (3) if those relationships were different if
small/big communities, we modelled the dynamics the temporal trends of food-web
structure ($dN$) in function of the temporal trends of community biomass ($dB$) and species
richness ($dR$), if the latter was positive of not (Inc) and with respectively the median
community biomass ($B_i$) and species richness ($R_i$)of the three first years of the temporal
series .

$dN = dB + B_i + dB \times B + Inc \times B_i + dB \times Inc \times B_i$

$dN = dR + R_i + dR \times R_i + Inc \times R_i + dR \times Inc \times R_i$

@@

  - $dN$: temporal trend of network structure and communities structure
  - $dB$: temporal trend of community (log) biomass
  - $dR$: temporal trend of (log) species richness 
  - $B_i$: median community biomass of the first three year
  - $R_i$: median species richness of the first three year
  - $Inc$: Is $dB > 0$?

In order to control for the uncertainties of the estimated temporal trends, we
weighted each temporal trends by the inverse of the product between the standard
error of the estimated trends, i.e. slopes, for the response and the explicative
variable.

@@

$N =  B + R + E_1 + E_2 $

@@

  - $N$: median network structure and communities structure
  - $B$: median community biomass
  - $R$: median species richness

@@

We also found in space that evenness of biomass was positively related to
community while eveness of individual number had no relation. It constrasts with
previous studies which found a negative relationship between biomass and eveness
of individual in marine and plant communities [@drobner_relation_1998;
@maureaud_biodiversityecosystem_2019] or studies that found more even plant
communities in terms of individual number display higher community biomass
[@wisley_biodiversity_2000].

We further found that the temporal trends of connectance was positively
linked to that one of community biomass, meaning that connectance increases through
time in a given site when community biomass increases through time and reversely.
This is in line with the fact that the fishes located at higher trophic level
also display a larger number of links as the size of the predation window
increases with the size of the fishes. This result is also in accordance with  
theoretical work showing that higher food-web connectance result in higher
community biomass [@thebaut_food-web_2003].

@@

To the difference with community biomass, the temporal trends evenness of
biomass and individual were positively related to the temporal trends of species
richness, meaning that as species richness temporally increase, the
distribution of biomass and abondance become more even. Our results indicate
that biomass trends are linked to few big individuals while richness trends are
linked to overall shift in dominance in communities.

@@

This result has profound implications for conservation. As more and more
studies report community biomass and richness trends [@hallmann_more_2017;
@ceballos_biological_2017], it is important to note that they might not be
equivalent in terms of consequences on the structure of the community. Further
studies should investigate the temporal trends of several dimensions of
community structure simultaneously because it drives many aspects of ecosystem
functioning.

@@

We found no case in which gain or losses of biomass and richness lead to
different relationship between the temporal dynamic of community structure and
the one of biomass and species richness. We could have imagine that
extinction/colonisation processes or immigration/extinction debt could have lead
to different relationships.

@@

```{r}
ti <- list()
for (i in c("log_rich_std", "w_trph_lvl_avg",  "piel_bm", "piel_nind", "ct_ff")) {
  ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]]) 
}
```

@@

```{r}
p_rich <- get_plot_fig1_2(
  predict_plot = predict_plot2,
  get_list = TRUE,
  rich_x = "log_rich_std",
  rich_y = c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std") 
  )$rich
names(p_rich) <- c(
  "ct_ff", "w_trph_lvl_avg", "piel_nind",
  "piel_bm", "log_bm_std")
#plot_grid(plotlist = p_rich)

@@

```{r}
fig2_left <- plot_grid(plotlist = p_rich, ncol = 1)
fig2_right <- plot_grid(plotlist = p_sp_rich, ncol = 1)
#plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)

@@

```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
# Make the label on two lines 
top_rich <- plot_grid(plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]), ncol = 2)
fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
fig2
```

@@

```{r}
loadd(model_log_bm_f3y_table_medium, model_log_rich_f3y_table_medium)
```

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% net_var_bm) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of 
      community biomass and the temporal trends of the network structure."
    ),
  label = "tab:aov-bm"

  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% net_var_rich) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
    ),
  label = "tab:aov-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium$reg_table %>% 
  filter(y %in% net_var_bm) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
  label = "tab:reg-bm"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium$reg_table %>%
  filter(y %in% net_var_rich) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of species richness and the temporal trends of
      the network structure."
    ),
  label = "tab:reg-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
rsq %>%
  rename(
    Response = y, Explicative = x, 
    `Squared R` = r.squared, `Adjusted squared R` = adj.r.squared
  ) %>% 
  select(Explicative, Response, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Squared and adjusted squared R for linear models of spatial relationships."),
  label = "tab:rsq"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
tab_sp_anova$log_bm_std %>%
  filter(y %in% net_var_bm) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of community
      biomass and the one of network structure."),
  label = "tab:aov-bm-sp"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
tab_sp_anova$log_rich_std %>%
  filter(y %in% net_var_rich) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the spatial variation of species
      richness and the one of network structure."),
  label = "tab:aov-rich-sp"
      ) %>% # 
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

table_rsq_sp %>%
  filter(Explicative %in% c("log_rich_std", "log_bm_std")) %>%
  mutate(
    Explicative = str_replace_all(Explicative, var_replacement()),
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "tab:rsq-sp"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")

>>>>

---
title: "Biomass and species richness temporal trends drives the assembly and the disassembly of food-web in natural fish assemblages"
author: Alain Danet, Maud Mouchet, Willem Bonnaffé, Elisa Thébault and Colin Fontaine
date: \today 
output:
  bookdown::pdf_document2:
    fig_caption: true 
    keep_tex: true
    toc: true
fontsize: 12pt
header-includes:
   - \usepackage{natbib}
   - \usepackage{float}
   - \usepackage[table]{xcolor}
   - \usepackage{multirow}
   - \usepackage{booktabs}
   - \usepackage{makecell}
   - \usepackage{setspace}
   - \doublespacing
   - \usepackage{lineno}
   - \linenumbers
geometry: margin=2cm
bibliography: references.bib
number_sections: true
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  cache = FALSE,
  collapse = TRUE,
  comment = "#>",
  #fig.dim = c(7, 7),
  fig.fullwidth = TRUE,
  fig.show = "hold",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  results = TRUE
)

@@

theme_set(mytheme)
options(knitr.table.format = "latex")
```
```{r}
net_var_bm <- c("log_rich_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
net_var_rich <- c("log_bm_std", "ct_ff", "w_trph_lvl_avg", "piel_bm",
      "piel_nind")
```

@@

Biodiversity affects ecosystem properties such as total biomass, productivity
and stability [@tilman_biodiversity_2014; @loreau_biodiversity_2001]. However,
current biodiversity is at risk, numerous
studies reported dramatic declines of population and community biomass
[@ceballos_biological_2017; @hallmann_more_2017; @albano_native_2021], as well
as ongoing extinction [@barnosky_has_2011]. Consequences of such trends on various
aspects of community structure are not well-known whereas numerous ecological studies
have shown that the different aspects of community structure are tightly linked [REF].

The temporal trends of species richness and community biomass are likely to
affect community structure. The positive link between Biodiversity and ecosystem
functioning shown in experimental studies predict that loss and gain of species
richness should respectively result in loss and gain of community biomass
[@tilman_biodiversity_2014; @pennekamp_biodiversity_2018]. But this relation is
not always found in natural settings [@grace_integrative_2016;
@li_relationship_2018; @maureaud_biodiversityecosystem_2019]. Numerous
studies find relation between species richness and evenness, but their disagree
on the sign of the relationships [@soininen_relationship_2012; @ma_species_2005;
@maureaud_biodiversityecosystem_2019], highlighting the diversity of assembly
processes in ecological communities.

The distribution and the number of ecological interactions, i.e. the structure
of ecological networks, also covaries with species richness and community
biomass. In food-webs, connectance, which measures the degree of generalism in a
network, has been theoretically shown to theoretically positively scale with
community biomass [@thebault_food-web_2003]. Connectance has been also shown to
be negatively related to species richness in empirical food-webs
[@dunne_network_2006]. Trophic level has also been shown to be positively linked
to total biomass in theoretical models [@wang_biodiversity_2018]. All together,
these studies show that the different dimensions of network structure are
closely linked.

The space for time substitution allows to use the studies mentioned above to
predict how changes in species richness or community biomass will in turn affect
community and network structure. The hypothesis that space can
surrogate space is often implicitly made in ecological studies. This method
began to be widely used in the early 20th century to infer the temporal
succession of vegetation from space variations [@pickett_space-for-time_1989]. It
supposes a homology between variations in space and in time i.e. that spatial
sequences corresponds to temporal sequences. This method have raised criticisms
[@damgaard_critique_2019], with studies showing analogous patterns in space and time
[@blois_space_2013] or not [@johnson_testing_2008; @adler_contrasting_2007].
Spatial turnover of species composition, dispersal limitation, disturbance and
stochastic processes have been hypothesised to be responsible for the failure of
space for time substitution [@adler_contrasting_2007; @blois_space_2013].

In this line, how community biomass and species richness temporal trends are linked to
change in food-web structure is still an open question, as well as if space for
time substitution works to infer consequences of species richness and community
biomass on food-web structure. The increasing availability of ecological
temporal series makes possible to assess those questions.

Using a standardized monitoring of fish freshwater communities on the period
1995-2018, we assessed the relationships among temporal trends of food-web
structure, trends of community biomass and trends in species richness.  
Moreover, we tested if the those relationships differs between communities that
loosed or gained biomass/species richness across time, reflecting potential
difference between disassembly and assembly processes. We finally assessed if
spatial relationships display the same patterns as temporal ones, to assess
the validity of space for time substitution.

@@

We characterized food-webs by its connectance, describing the degree of
generalism in a network [@dunne_network_2006; @delmas_analysing_2019]. It is
computed as the ratio between the actual number of links and the number of
potential links ($C = \frac{L}{S(S-1)}$, with $L$ being the number of links and
$S$ the number of trophic species). We also computed the average trophic level,
weighted by the biomass of the trophic species. The trophic level of a trophic
species is computed recursively as 1 added to the mean trophic level of the
preys that it consumes.

@@

```{r}
loadd(full_data2, st_mono_trends_combined_list)
```
```{r}
nb_st <- unique(full_data2$station) %>% length
rm(full_data2)
nb_st_var <- map_dbl(st_mono_trends_combined_list$station, length)
names(nb_st_var) <- st_mono_trends_combined_list$variable
```

@@

With the goal to characterize the links among the temporal variations of network
and community structure and the temporal variations of community biomass and
species richness, we characterized the temporal trajectories of network and
community structure at each site. We used a method based on second order
polynomial which allows to assess both the direction and the monotony of
temporal trends [@rigal_method_2020]. To avoid complex variations of biomass and
species richness, we selected the stations that displayed monotonic trends for
these variable. Over the `r nb_st` stations, the selection procedure resulted
in respectively `r nb_st_var["log_bm_std"]` stations  and `r nb_st_var["log_rich_std"]`
for community biomass and species richness analysis.

@@

With the aim to test (1) the relationship among the temporal dynamics of network
structure from one side and species richness and community biomass from another
side, (2) if those relationships were different if the communities were
assembling or disassembling, (3) if those relationships were different if
small/big communities, we modelled the dynamics the temporal trends of food-web
structure ($dN$) in function of the temporal trends of community biomass ($dB$) and species
richness ($dR$), if the latter was positive of not (Inc) and with respectively the median
community biomass ($B_i$) and species richness ($R_i$)of the three first years of the temporal
series.

$dN = dB + B_i + dB \times B + Inc_B \times B_i + dB \times Inc_B \times B_i$

$dN = dR + R_i + dR \times R_i + Inc_R \times R_i + dR \times Inc_R \times R_i$

@@

  - $dN$: temporal trend of network structure and communities structure
  - $dB$: temporal trend of community (log) biomass
  - $dR$: temporal trend of (log) species richness 
  - $B_i$: median community biomass of the first three year
  - $R_i$: median species richness of the first three year
  - $Inc_B$: Is $dB > 0$?
  - $Inc_R$: Is $dR > 0$?

In order to control for the uncertainties of the estimated temporal trends, each
temporal trend was weighted by the inverse of the product of the standard errors of the
estimated trends, i.e. slopes for the response and the explicative
variable.

@@

$N =  B + R + E_1 + E_2$

@@

  - $N$: median network structure and communities structure
  - $B$: median community biomass
  - $R$: median species richness 
  - $E_1$: PCA1 related to stream size
  - $E_2$: PCA2 related to average temperature and average BOD

@@

We also found in space that evenness of biomass was positively related to
community while eveness of individual number had no relation. It constrasts with
previous studies which found a negative relationship between biomass and eveness
of individual in marine and plant communities [@drobner_relation_1998;
@maureaud_biodiversityecosystem_2019] or studies that found more even plant
communities in terms of individual number display higher community biomass
[@wilsey_biodiversity_2000].

We further found that the temporal trends of connectance was positively
linked to that one of community biomass, meaning that connectance increases through
time in a given site when community biomass increases through time and reversely.
This is in line with the fact that the fishes located at higher trophic level
also display a larger number of links as the size of the predation window
increases with the size of the fishes. This result is also in accordance with  
theoretical work showing that higher food-web connectance result in higher
community biomass [@thebault_food-web_2003].

@@

To the difference with community biomass, the temporal trends of evenness of
biomass and individual were positively related to the temporal trends of species
richness, meaning that as species richness temporally increase, the
distribution of biomass and abondance become more even. Our results indicate
that biomass trends are linked to few big individuals while richness trends are
linked to overall shift in dominance in communities.

@@

This result has profound implications for conservation. As more and more
studies report community biomass and richness trends [@hallmann_more_2017;
@ceballos_biological_2017], it is important to note that they might not be
equivalent in terms of consequences on the structure of the community. Further,
studies should investigate the temporal trends of several dimensions of
community structure simultaneously because it drives many aspects of ecosystem
functioning.

@@

We found no case in which gain or losses of biomass and richness lead to
different relationship between the temporal dynamic of community structure and
the one of biomass and species richness. We could have imagined that
extinction/colonisation processes or immigration/extinction debt could have lead
to different relationships.

@@

```{r}
ti <- list()
for (
  i in c("log_rich_std", "w_trph_lvl_avg", "piel_bm", "piel_nind", "ct_ff")
  ) {
  ti[[i]] <- list(p_bm[[i]], p_sp_bm[[i]])
}
```

@@

```{r}
p_rich <- get_plot_fig1_2(
  predict_plot = predict_plot2,
  get_list = TRUE,
  rich_x = "log_rich_std",
  rich_y <- c("ct_ff", "w_trph_lvl_avg", "piel_nind", "piel_bm", "log_bm_std")
  )$rich
names(p_rich) <- c(
  "ct_ff", "w_trph_lvl_avg", "piel_nind",
  "piel_bm", "log_bm_std")
#plot_grid(plotlist = p_rich)

@@

```{r}
fig2_left <- plot_grid(plotlist = p_rich, ncol = 1)
fig2_right <- plot_grid(plotlist = p_sp_rich, ncol = 1)
# plot_grid(plotlist = list(p_bm[[1]], p_sp_bm[[1]], ), ncol = 1)

@@

```{r rich, fig.height = 12, fig.cap=fig_rich_cap}
# Make the label on two lines
top_rich <- plot_grid(
  plotlist = c(trich[[1]], trich[[2]], trich[[3]], trich[[4]], trich[[5]]),
  ncol = 2)
fig2 <- plot_grid(top_rich, p_rich[[6]], ncol = 1, rel_heights = c(1, .1))
fig2
```

@@

```{r}
model_log_bm_f3y_table_medium[["anova_table"]] %>%
  filter(y %in% net_var_bm) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(.,
    booktabs = TRUE,
    caption =
      paste0(
      "ANOVA results for the links between the temporal trends of
      community biomass and the temporal trends of the network structure."
    ),
  label = "aov-bm"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium[["anova_table"]] %>% 
  filter(y %in% net_var_rich) %>%
  select(-mod_summary_table) %>%
  format_anova_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "ANOVA results for the links between the temporal trends of species
      richness and the temporal trends of the network structure."
    ),
  label = "aov-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_bm_f3y_table_medium$reg_table %>% 
  filter(y %in% net_var_bm) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of community biomass and the temporal trends
      of the network structure."),
  label = "reg-bm"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
model_log_rich_f3y_table_medium$reg_table %>%
  filter(y %in% net_var_rich) %>%
  format_reg_table() %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Regression coefficients for the linear models explaining the links
      between the temporal trends of species richness and the temporal trends of
      the network structure."
    ),
  label = "reg-rich"
  ) %>%
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
rsq %>%
  rename(
    Response = y, Explicative = x, 
    `Squared R` = r.squared, `Adjusted squared R` = adj.r.squared
  ) %>% 
  select(Explicative, Response, everything()) %>%
  kable(., booktabs = TRUE,
    caption = 
      paste0(
      "Squared and adjusted squared R for linear models of spatial relationships."),
  label = "rsq"
      ) %>% # 
  kable_styling(latex_options =c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

```{r}
tab_sp_anova$log_bm_std %>%
  filter(y %in% net_var_bm) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "ANOVA results for the links between the spatial variation of community
      biomass and the one of network structure."),
  label = "aov-bm-sp"
  ) %>%
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

```{r}
tab_sp_anova$log_rich_std %>%
  filter(y %in% net_var_rich) %>%
  mutate(
    y = str_replace_all(y, var_replacement()),
    term = str_replace_all(term, var_replacement()),
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "ANOVA results for the links between the spatial variation of species
      richness and the one of network structure."),
  label = "aov-rich-sp"
      ) %>% #
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```

@@

table_rsq_sp %>%
  filter(Explicative %in% c("log_rich_std", "log_bm_std")) %>%
  mutate(
    Explicative = str_replace_all(Explicative, var_replacement()),
    Response = str_replace_all(Response, var_replacement())
  ) %>%
  kable(., booktabs = TRUE,
    caption =
      paste0(
      "Marginal and conditional squared R for spatial models."),
  label = "rsq-sp"
      ) %>% #
  kable_styling(latex_options = c("scale_down", "stripped")) %>%
  collapse_rows(columns = 1, valign = "top")
```
